---
title: "Ten Simple Rules"
author: "Michelle Wille"
date: "25/11/2021"
output: 
  html_document:
      toc: true
      number_sections: true
      code_folding: hide
---

# Set up

```{r, warning=FALSE, message=FALSE}

setwd("~/Desktop/USyd Post Doc/2022_TenSimpleRules/2021 papers")

library(ggplot2)
library(dplyr)
library(reshape2)

dat <- read.csv("DataSheet_2021_Papers.csv",na.strings=c("", "NA"), header=TRUE,sep=",")
```

# Reformat and clean
```{r, warning=FALSE, message=FALSE}
# convert from wide to long
dflong<-melt(dat, id.vars=c("Paper", "Host"))

#convert number to answer
dflong$Response<-dflong$value
dflong$Response<-ifelse(dflong$Response=="1", "1_Not_included", dflong$Response)
dflong$Response<-ifelse(dflong$Response=="2", "2_Partially_included", dflong$Response)
dflong$Response<-ifelse(dflong$Response=="3", "3_Included", dflong$Response)

```

# plotting
```{r, warning=FALSE, message=FALSE}
#aggregate
tmp<-aggregate(Paper~Response+variable, data=dflong, FUN=length)

#plot
ggplot(tmp, aes(x=Paper, y=variable, fill=Response)) + 
  geom_bar(stat="identity", position = position_fill(reverse = TRUE))+
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
 scale_y_discrete(limits=rev)

#aggregate
tmp<-aggregate(Paper~Host, data=dat, FUN=length)

#plot
ggplot(tmp, aes(x="", y=Paper, fill=Host))+
geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_void()